Understanding the Causal Impact of Bike Lane Installation on Urban Cycling Adoption

### 2024-12-13 paper/paper.qmd
fixed table formating, removed stars

```{r}
#| label: fig-avg-monthly-ridership
#| fig-cap: "Average ridership by relative months to treatment"
#| echo: false
#| warning: false
#| message: false

@@

ggplot(ridership_by_month, aes(x = relative_month, y = rides, color = metric)) +
  geom_line() +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.5) +
  labs(
    x = "Months Relative to Treatment",
    y = "Average Monthly Rides",
    color = "Metric"
  ) +
  scale_color_manual(
    values = c("grey10", "blue"),
    labels = c("Raw Rides", "Seasonally Adjusted")
  ) +
  theme_minimal() +
  theme(legend.position = "top",
        panel.grid.major = element_line(color = "gray85", linewidth = 0.35)
  ) +
  facet_wrap(~treatment, 
             labeller = labeller(treatment = c("TRUE" = "Treatment", "FALSE" = "Control")))

@@

```{r}
#| label: fig-treatment-control-count
#| fig-cap: "Total Bikeway Count in Control Vs. Treatment Group"
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-infra-type
#| fig-cap: "Infrastrucutre Type Distribution between Control and Treatment Group"
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-treatment-type-total
#| fig-cap: "Number of New-Installations Vs Upgrades in Treatment Group"
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-parallel
#| fig-cap: "Parallel Trends Test: Average Monthly Rides in Pre-Treatment Period"
#| echo: false
#| warning: false
#| message: false

@@

modelsummary(
  list("Main DiD Model" = main_did),
  stars = TRUE,
  gof_map = c("nobs", "r.squared", "adj.r.squared")
)
```

@@

# Randomly assign treatment
set.seed(778)

@@

modelsummary(
  list("Placebo Test - Random Assignment" = placebo_random_did),
  stars = TRUE,
  gof_map = c("nobs", "r.squared", "adj.r.squared")
)

@@

modelsummary(
  list("Heterogeneous Effects - Bikeway Type" = did_hetero_lane),
  stars = TRUE,
  gof_map = c("nobs", "r.squared", "adj.r.squared"),
  coef_map = c(
  "period::treatment:treatment_infra::Control" = "Treatment x Control",
  "period::treatment:treatment_infra::Treated-OnRoad" = "Treatment x Treated-OnRoad",
  "period::treatment:treatment_infra::Treated-Protected" = "Treatment x Treated-Protected",
  "period::treatment:treatment_infra::Treated-Shared" = "Treatment x Treated-Shared",
  "period::post:treatment_infra::Control" = "Post x Control",
  "period::post:treatment_infra::Treated-OnRoad" = "Post x Treated-OnRoad",
  "period::post:treatment_infra::Treated-Protected" = "Post x Treated-Protected",
  "period::post:treatment_infra::Treated-Shared" = "Post x Treated-Shared"
  ),
  output = "latex"
)
```

@@

modelsummary(
  list("Heterogeneous Effects - Treatment Type" = did_hetero_treat_type),
  stars = TRUE,
  gof_map = c("nobs", "r.squared", "adj.r.squared"),
  coef_map = c(
    "period::treatment:sub_treatment_type::Upgraded" = "Treatment x Upgraded",
    "period::treatment:sub_treatment_type::Newly-Installed" = "Treatment x Newly Installed",
    "period::post:sub_treatment_type::Upgraded" = "Post x Upgraded",
    "period::post:sub_treatment_type::Newly-Installed" = "Post x Newly Installed"
  ),
  output = "latex"
)
```

@@

# Appendix {.unnumbered}
# Idealized Survey Methodology {#sec-ideal-survey}
## Survey Objectives
Following Stantcheva's [-@Stantcheva2023] framework, we recognize that surveys are not merely for data colletion, but rather "creating the process that will generate the data." The goal of our idealized survey is to measure otherwise "invisible factors" regarding cycling infrastructures influence on bike share usage, specifically:

@@

# Additional Tables & Figures {#sec-additional-figures}
```{r}
#| label: tbl-sample-data
#| tbl-cap: "Sample of processed dataset for DiD Model"
#| echo: false
#| warning: false
#| message: false

>>>>

```{r}
#| label: fig-avg-monthly-ridership
#| fig-cap: "Average bike share ridership by relative months to bikeway treatment period"
#| echo: false
#| warning: false
#| message: false

@@

ggplot(ridership_by_month, aes(x = relative_month, y = rides, color = metric)) +
  geom_line() +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.5) +
  labs(
    x = "Months Relative to Treatment",
    y = "Average Monthly Rides",
    color = "Metric"
  ) +
  scale_color_manual(
    values = c("grey10", "blue"),
    labels = c("Raw Rides", "Seasonally Adjusted Rides")
  ) +
  theme_minimal() +
  theme(legend.position = "top",
        panel.grid.major = element_line(color = "gray85", linewidth = 0.35)
  ) +
  facet_wrap(~treatment, 
             labeller = labeller(treatment = c("TRUE" = "Treatment", "FALSE" = "Control")))

@@

```{r}
#| label: fig-treatment-control-count
#| fig-cap: "Total bikeway count in control and treatment group"
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-infra-type
#| fig-cap: "Bikeway type distribution between control and treatment group"
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-treatment-type-total
#| fig-cap: "Number of new-installations and upgrades of bikeways in treatment Group"
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-parallel
#| fig-cap: "Parallel Trends Test: Average monthly rides in pre-treatment period"
#| echo: false
#| warning: false
#| message: false

@@

modelsummary(
  list("Main DiD Estimates" = main_did),
  statistic = "s.e. = {std.error}, p = {p.value}",
  gof_map = c("nobs", "r.squared", "adj.r.squared"),
  coef_map = c(
    "period::post:treatment" = "Post-Treatment Effect",
    "period::treatment:treatment" = "During-Treatment Effect"
  ),
)
```

@@

set.seed(778) # set same seed as model_data implementation script

@@

modelsummary(
  list("Placebo Test Estimates" = placebo_random_did),
  statistic = "s.e. = {std.error}, p = {p.value}",
  gof_map = c("nobs", "r.squared", "adj.r.squared"),
  coef_map = c(
    "period::post:placebo_treatment" = "Post-Placebo Treatment Effect",
    "period::treatment:placebo_treatment" = "During-Placebo Treatment Effect"
  ),
)

@@

modelsummary(
  list("Heterogenous Estimates by Bikeway Type" = did_hetero_lane),
  statistic = "s.e. = {std.error}, p = {p.value}",
  gof_map = c("nobs", "r.squared", "adj.r.squared"),
  coef_map = c(
  "period::treatment:treatment_infra::Control" = "During-Treatment Effect: Control Bikeways",
  "period::treatment:treatment_infra::Treated-Shared" = "During-Treatment Effect: Shared Roadways",
  "period::treatment:treatment_infra::Treated-OnRoad" = "During-Treatment Effect: On-Road Lanes",
  "period::treatment:treatment_infra::Treated-Protected" = "During-Treatment Effect: Protected Lanes",
  "period::post:treatment_infra::Control" = "Post-Treatment Effect: Control Bikeways",
  "period::post:treatment_infra::Treated-Shared" = "Post-Treatment Effect: Shared Roadways",
  "period::post:treatment_infra::Treated-OnRoad" = "Post-Treatment Effect: On-Road Lanes",
  "period::post:treatment_infra::Treated-Protected" = "Post-Treatment Effect: Protected Lanes"
  )
)
```

@@

modelsummary(
  list("Heterogeneous Estimates by Implementation" = did_hetero_treat_type),
  statistic = "s.e. = {std.error}, p = {p.value}",
  gof_map = c("nobs", "r.squared", "adj.r.squared"),
  coef_map = c(
    "period::treatment:sub_treatment_type::Upgraded" = "During-Treatment Effect: Upgraded",
    "period::treatment:sub_treatment_type::Newly-Installed" = "During-Treatment Effect: Newly Installed",
    "period::post:sub_treatment_type::Upgraded" = "Post-Treatment Effect: Upgraded",
    "period::post:sub_treatment_type::Newly-Installed" = "Post-Treatment Effect: Newly Installed"
  )
)
```

@@

# Appendix {-}
# Idealized Survey Methodology {#sec-ideal-survey}
## Survey Objectives
Following Stantcheva's [-@Stantcheva2023] framework, we recognize that surveys are not merely for data colletion, but rather "creating the process that will generate the data." The goal of our idealized survey is to measure otherwise "invisible factors" regarding cycling infrastructures influence on bike share usage, specifically:

@@

# Additional Tables & Figures {#sec-additional-figures}
```{r}
#| label: tbl-sample-data
#| tbl-cap: "Sample of processed dataset for DiD Model and analysis"
#| echo: false
#| warning: false
#| message: false
